---
title: "Tables"
author: "Barry DeCicco"
date: "June 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
```

## R Markdown

In his Knitr in a Knutshell, Dr. Karl Broman introduces: kable, pander, and xtable and I have especially enjoyed using the first two:

kable: Within the knitr package - not many options but looks nice with ease.
pander: Within the pander package - has many more options and customization. Useful for bold-ing certain values (e.g. values below a threshold).
kable and pander tables are nice as they are useful for making non-interactive tables.
xtable gives more control.
DT gives interactivity.

```{r kable_1}

kable(head(mtcars, n = 4)) # kable table with 4 rows

```




```{r pander_table_1, echo=TRUE}

# Pander table
# install.packages("pander") # install pander first
library(pander)
pander(head(mtcars, n = 4))

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


```{r data_table_1}

# DT table = interactive
# install.packages("DT") # install DT first - already done.
library(DT)
datatable(head(mtcars, n = nrow(mtcars)), options = list(pageLength = 5)) 

```
```{r xtable_1} 

# xtable gives more control.




```

